Clique and Constraint Models for Maximum Common (Connected) Subgraph Problems

### 2016-06-13 paper/paper.tex
Find -> Finding
Applications

\section{Find Maximum Common Connected Subgraphs}\label{mccs}

In many applications, the common subgraph must be connected
\cite{DBLP:journals/tcs/Koch01,DBLP:journals/jcamd/RaymondW02a,DBLP:conf/mco/VismaraV08,Ehrlich:2011}.
Adding the connectedness requirement makes certain special cases solvable in polynomial time,
including outerplanar graphs of bounded degree \cite{DBLP:journals/algorithms/AkutsuT13} and trees
\cite{droschinsky_et_al:LIPIcs:2016:xxxx}, but the general case remains \NP-hard. As illustrated in
\cref{figure:mcsexample}, the MCCS cannot be deduced from the MCS: we need to ensure connectedness
during search. In \cref{mccs-cp}, we show that in CP this may be done in two different ways that
may be combined, and we show in \cref{mccs-cp-eval} that the best results are obtained when
combining them. In \cref{mccs-clique}, we introduce a new way for ensuring connectedness in a
clique-based approach. Finally, we compare CP and our clique-based approach in \cref{mccs-eval}.

>>>>

\section{Finding Maximum Common Connected Subgraphs}\label{mccs}

In many applications, the common subgraph must satisfy some additional constraints. These
constraints are usually handled in a straightforward way in CP, by branching rules and/or constraint
propagation. In clique-based approaches, some constraints may be easily handled by modifying the
definition of the association graph---for example, constraints on pairs of vertices that may be
matched are handled by removing inconsistent pairs from $\operatorname{V}(G \modularproduct H)$.
However, more global constraints cannot be handled by modifying the definition of the association
graph.

In this paper, we focus on the connectedness constraint, which occurs in many applications
\cite{DBLP:journals/tcs/Koch01,DBLP:journals/jcamd/RaymondW02a,DBLP:conf/mco/VismaraV08,Ehrlich:2011}.
Adding the connectedness requirement makes certain special cases solvable in polynomial time,
including outerplanar graphs of bounded degree \cite{DBLP:journals/algorithms/AkutsuT13} and trees
\cite{droschinsky_et_al:LIPIcs:2016:xxxx}, but the general case remains \NP-hard. As illustrated in
\cref{figure:mcsexample}, the MCCS cannot be deduced from the MCS: we need to ensure connectedness
during search. In \cref{mccs-cp}, we show that in CP this may be done in two different ways that
may be combined, and we show in \cref{mccs-cp-eval} that the best results are obtained when
combining them. In \cref{mccs-clique}, we introduce a new way for ensuring connectedness in a
clique-based approach. Finally, we compare CP and our clique-based approach in \cref{mccs-eval}.
